A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Edits up to Concept Mapping

\subsubsection*{Extracting Latent Features}
We may now construct a synthetic $N \times N$ user-item matrix $M$ with rows
representing items and columns representing users, which are in fact the
stationary distributions discovered from our random walks. This matrix has at
least one notable advantage over most real user-item matrices---it is not
sparse.  Rather, each synthetic user has a finite value associated with every
item that is reachable from its origin item in the graph. Unlike the typical CF
scenario, we may therefore employ SVD as our matrix factorization technique
since our user-item matrix is virtually complete (i.e. nearly void of empty
entries).  Using SVD, we factor our user-item matrix as
\begin{align}
M = U \Sigma V^T,
\end{align}
where the rows of the $N \times N$ matrix $U$ and the $N \times N$ matrix $V$
are the items and users represented in an $N$-dimensional concept space,
respectively, and the $N$ diagonal entries of $\Sigma$ are the singular values
associated with each concept.

@@

Figures 1 and 2 show the top and bottom most relevant items for two of the sixteen
concepts learned for the Women's Dresses category. Note that concepts learned by
SVD range from positive to negative, representing the two extremes of the
concept.

>>>>

\subsubsection*{Extracting Latent Features}
We may now construct a synthetic $N \times N$ item-user matrix $M$ with rows
representing items and columns representing users, which are in fact the
stationary distributions discovered from our random walks. This matrix has at
least one notable advantage over most real item-user matrices---it is not
sparse.  Rather, each synthetic user has a finite value associated with every
item that is reachable from its origin item in the graph. Unlike the typical CF
scenario, we may therefore employ SVD as our matrix factorization technique
since our item-user matrix is virtually complete (i.e. nearly void of empty
entries).  Using SVD, we factor our item-user matrix as
\begin{align}
M = U \Sigma V^T,
\end{align}
where the rows of the $N \times N$ matrix $U$ and the $N \times N$ matrix $V$
are the items and users represented in an $N$-dimensional concept space,
respectively, and the $N$ diagonal entries of $\Sigma$ are the singular values
associated with each concept.

@@

Figures 1 and 2 show the top and bottom most relevant items for two of the sixteen
concepts learned in this way on the Women's Dresses category. Note that concepts
learned by SVD range from positive to negative, representing the two extremes of
the concept, therefore it is relevant to look at both the top and bottom items.
